\textbf{International Transport costs:\\New Findings from modeling additive costs}\\Online Appendix (Not for Publication)

### 2021-11-24 redaction/JEGeo/revision_JEGeo/revised_article/Online_Appendix/online_appendix_DHP_rev1.tex
changement papier + OA - ENCORE A RELIRE

Two main results emerge. First, given the constraints on the sample selection for quantities, the estimation based on quantity can only be run on a reduced sample. In contrast to the aggregation and the separability issues, these restrictions strongly limit both the number of sectors and of countries covered, and do also impact the value of trade flows covered.
A related argument is illustrated by Figure \ref{graph_Share_of_discrete_goods.png}. After computing the share of discrete goods per 5-digit SITC import in 2009, we have used the changing composition of US imports to approximate the share of discrete goods in the total value of US imports on a yearly basis. According to this rough approximation, discrete goods are between 23\% and 52\% of US imports, reaching a value only above 50\% for two years. Switching to a per-unit approach would hence mean a marked reduction in the trade flows coverage, thereby limiting the general scope of our estimates.

@@

@@

As reported in Figures \ref{fig:totalTC_compeffects_excl_manuf} and \ref{fig:totalTC_compeffects_excl_primary}, both the ``ceteris paribus'' transport costs and the raw measure have regularly declined over the period in both sectors, by roughly the same order of magnitude (50\% in air, 60\% in vessel for overall transport costs, panels (c) and (f)). However the role of trade composition effects in accounting for this trend pattern differs depending on the sector.\\
In the manufacturing sector, Figure \ref{fig:totalTC_compeffects_excl_manuf} reports a very similar time trend decomposition than what is obtained on the whole range of goods (Figure \ref{fig:totalTC_compeffects_excl}).  In vessel transport, most of the decrease can be imputed to the reduction of``ceteris paribus'' transport costs (the blue continuous line): trade composition effects playing virtually no role (Figure \ref{fig:totalTC_compeffects_excl_manuf}, right-hand panels (d), (e) and (f)). Trade composition effects matter more in air transport (Figure \ref{fig:totalTC_compeffects_excl_manuf}, left-hand panels (a), (b) and (c)), primarily in the ad-valorem component. As for the whole range of flows, the 60\% decrease in the raw transport costs in vessel can de decomposed in a 50\% decrease in the ``ceteris paribus'' transport costs, the 10\% remaining to trade composition effects.

The situation is different in the primary sector. In this case, in air transport the composition effects matter more (Figure \ref{fig:totalTC_compeffects_excl_primary}, left-hand panels (a), (b) and (c)), while we observe not much role for them in vessel transport (Figure \ref{fig:totalTC_compeffects_excl_primary}, right-hand panels (d), (e) and (f)).

>>>>

Two main results emerge. First, given the constraints on the sample selection for quantities, the estimation based on quantity can only be run on a reduced sample. In contrast to the aggregation and the separability issues, these restrictions strongly limit both the number of sectors and of countries covered, and do also impact the value of trade flows covered. This raises a non-trivial sample selection bias that would limit the general scope of our transport costs estimates.

@@

In a related manner, restricting the sample to denumerable goods would defeat our purpose of estimating international transport costs for the whole range of US imports. This is illustrated in Figure \ref{graph_Share_of_discrete_goods.png}. After computing the share of discrete goods per 5-digit SITC import in 2009, we have used the changing composition of US imports to approximate the share of discrete goods in the total value of US imports on a yearly basis. According to this rough approximation, discrete goods are between 23\% and 52\% of US imports, reaching a value only above 50\% for two years. Switching to a per-unit approach would hence mean a marked reduction in the trade flows coverage, thereby limiting the general scope of our estimates.

@@

As reported in Figures \ref{fig:totalTC_compeffects_excl_manuf} and \ref{fig:totalTC_compeffects_excl_primary}, both the ``ceteris paribus'' transport costs and the raw measure have regularly declined over the period in both sectors, by roughly the same order of magnitude (50\% in air, 60\% in vessel for overall transport costs, panels (c) and (f)). However the role of trade composition effects in accounting for this trend pattern differs depending on the sector.\\
In the manufacturing sector, Figure \ref{fig:totalTC_compeffects_excl_manuf} reports a very similar time trend decomposition than what is obtained on the whole range of goods (Figure \ref{fig:totalTC_compeffects_excl}).  One can further notice that in vessel transport, composition effects play virtually no role at the end of the period, as most of the decrease can be imputed to the reduction of ``ceteris paribus'' transport costs (the blue continuous line)

The situation is different in the primary sector. In air transport, the role of composition effects exhibits an irregular pattern over time. They dampen the reduction in pure transport costs up to the 2000s. Afterwards, they conversely more than compensate the increase in pure transport costs (Figure \ref{fig:totalTC_compeffects_excl_primary}, left-hand panels (a), (b) and (c)). In vessel transport, the composition effects play a limited role in the primary sector as for the whole range of goods matter (Figure \ref{fig:totalTC_compeffects_excl_primary}, right-hand panels (d), (e) and (f)), by slightly amplifying the reduction in the pure transport costs in both cases.
